---

output: html_document
---



#This is an analysis of the `r Name_project` project



```{r, echo=FALSE}

summary (as.factor(metadata$groupingvar))

numberofvariables = (length(names(behav_gp))-3)* nrow (Timewindows)
numberofvariables = trunc(numberofvariables/3)


```
The data is grouped by `r Projects_metadata$group_by `.
Data transformation: `r calcul_text`.


---


We grouped the variables following the `r groupingby` argument to get `r length(names(behav_gp))-3` behavior categories. We used the folowing time windows and got `r length(names(behav_gp))-3` x `r nrow (Timewindows)` = `r (length(names(behav_gp))-3)* nrow (Timewindows)` variables :

```{r, results='asis', echo=FALSE}
pander::pandoc.table(Timewindows)
```
Note that the last window might be truncated if not all dataset is achieving 900 min after light on.

To plot the data, we ran a random forest to choose variables and an ica on these most important variables


```{r}
print (pls)
```





#SVM

We splitted the data in binomes, train a svm with 10 data points per group and test the accuracy of the model on the rest of the data. Here we report the accuracy of the model for each binome. A value above 3 is a good indication of a significant difference between the groups.
 


```{r, echo=FALSE}
p1
p2
p3

```











